\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-04 casestudies.tex
simplified inh fig for AI case study
mention extraction

@@

The other two families then extend \lsti{ImpGAI}.
Family \lsti{ImpTyping} (\textasciitilde200~LOC) is an abstract
interpreter that does type inference~\cite{cousot1997types}.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural number arithmetic,
and instantiates the generic abstract interpreter to perform constant propagation.
%
Gallina code generated for these two families are runnable;
they are put to test over simple queries.

>>>>

\begin{wrapfigure}[13]{r}{0.13\textwidth}
\includegraphics[scale=.68]{graphics/ai-casestudy.pdf}
\end{wrapfigure}

@@

The other two families then extend \lsti{ImpGAI}.
Family \lsti{ImpTI} (\textasciitilde200~LOC) is an abstract
interpreter that does type inference~\cite{cousot1997types}.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural number arithmetic,
and instantiates the generic abstract interpreter to perform constant propagation.

Our implementation of family polymorphism retains the computation
ability of the host proof assistant;
Gallina code generated for \lsti{ImpTI} and \lsti{ImpCP} are directly
runnable in Coq.
The two abstract interpreters can be extracted into OCaml;
we put them to test over simple queries.
